Mirror Match: Reliable Feature Point Matching Without Geometric Constraints

### 2013-08-01 text/clustering.tex
Clustered and bibliography from submitted

\documentclass[conference]{IEEEtran}
%\documentclass{article}
\usepackage{footnote}
%\usepackage[font={small}]{caption}
\usepackage{sidecap}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
\usepackage[stable]{footmisc}
\usepackage{caption}
\usepackage{adjustbox}
\usepackage{subcaption}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amssymb}

@@

\title{Reliable feature point matching without the use of geometric 
constraints}
%\author{Jonas Arnfred and what to put here exactly?}

\maketitle
\begin{abstract}
Many algorithms have been proposed to solve the problem of matching 
feature points in two or more images using geometric assumptions to 
increase the robustness of the matching. However very little work 
addresses the case where these assumptions might not hold true. In 
particular few methods address the problem of reliable matching in cases 
where we do not know if two images have any corresponding areas or 
objects. In this paper we propose two algorithms for matching feature 
points without the use of geometric constraints. The first makes use of 
the fact that any match between two images should be better than all 
possible matches within the image itself. The second algorithm extends 
this idea by using community structure in the similarity graph of 
feature points to reliably find correspondences. To evaluate the 
algorithms experimentally we introduce a set of 8 image pairs all 
containing viewport changes and a simple method to generate a large 
amount of test cases based on these 8 pairs. The experimental results 
show that the proposed algorithm, overall, is superior to traditional 
approaches in finding correct correspondences.

@@

at the geometric configuration of the feature points and match them 
according to assumptions made about the geometric relationship between 
the images matched. These assumptions are then used to create 
constraints on the matches such as angular constraints 
\cite{kim2008efficient}, epipolar constraints \cite{torr2000mlesac}, 
\cite{chum2005matching} and pairwise constraints \cite{choi2009robust}, 
\cite{leordeanu2005spectral}.

@@

%only consider matches that aren't deviating too much with respect to 
%the average angle and distancen as considered by 
%\cite{kim2008efficient}.  This performs well in situations where no 
%camera rotation occurs between the two images, but fails when this 
%assumption isn't met. Various scenarios have been proposed to improve 
%on this simple assumption such as epipolar constraints 
%(\cite{torr2000mlesac}, \cite{chum2005matching}) and pairwise 
%constraints (\cite{choi2009robust}, \cite{leordeanu2005spectral}). The 
%Epipolar constraint carries the assumption that the two images matched 
%are related by an affine transformation. That is, there is no relative 

@@

Alternatively we can pick out different areas in each image and pair 

@@

not fall within paired areas. Examples include \cite{das2008event} and 
\cite{wu2011robust}.

@@

In practice however, there are many situations where using the geometry 
of the image to filter correspondences is not possible, such as object 
recognition where adjacent objects in one photo might be separated in 
another. Another example is images that do not overlap where algorithms 
might still find matches adhering to the imposed geometric constraints.
In addition methods using geometric constraints all require an initial 
set of correspondences. If this set of correspondences is narrowed down 
to a set with a higher ratio of correct matches the result of the 
geometric matching will benefit in terms of speed and accuracy. Finally 
some use cases might require a performance that can't be achieved by a 
more complex geometric method where simple non geometric methods might 
be able to provide sufficient matching accuracy with a smaller 
performance penalty.

There are a relatively small number of algorithms proposed to solve the 
matching problem without involving geometric constraints. Traditionally 
the feature points of two images have been matched by comparing every 
feature point of one image with all feature points of the other and 
finding the best matches based on the similarity of the descriptors.  
With the introduction of the SIFT features \cite{lowe2004sift}, Lowe 
proposes an alternative measure where the uniqueness of a given match is 
found by looking at the two nearest neighbors of each feature point and 
calculating a match score by the ratio of similarities. Ranking the 
scores by their uniqueness and picking the $n$ best produces a set of 
correspondences that are distinctly matched across the two images. This 
method will be referred to as \emph{SIFT} in this paper.

In turn the two methods proposed in this paper are inspired by a simple 
but novel idea. If we have two images and a given feature point in the 
first image is better matched with other feature points from the 
\emph{same} image than points in the other image, then any matches from 
this feature point to points in the other image is deemed unreliable and 
discarded.  This approach carries no implicit assumptions about the 
geometric consistency of matches and can as such easily be extended with 
other geometric solutions when appropriate.

%Based on this idea the two proposed methods find reliable matches as 
%follows:
%\begin{itemize}
%\item[]{\emph{Mirror Match (MM)}: Match features using the gold standard 
%		algorithm\cite[p. 114]{multipleView} ranked by similarity and 
%		thresheld by uniqueness\cite{lowe2004sift}.  However instead of 
%		matching features from one image with features in another, we 
%	match every feature with all other features of the two images 
%combined. Only matches from one image to the other are returned.}
%\item[]{\emph{Mirror Match with Clustering (MMC)}: Take the combined set 
%		of feature points from both images and cluster these points 
%		according to their descriptors. Given a resulting partition of 
%		points, no matches are returned if it contains only feature 
%	points from one image. If the partition contains points from both 
%images, \emph{Mirror Match} is used to find the best matches within the 
%partition.}
%\end{itemize}
%%
%Matching feature points against the entire set of points from both 
%images ensures that the distinctiveness of a returned correspondence is 
%higher. In almost all cases\footnote{Exceptions would include cases 
%where we want to find all particular points in a pattern and other use 
%cases where the correspondence isn't assumed to be unique}, a good 
%match between two images is unambiguous in the sense that there are no 
%other equally good potential matches to the same point.  This is the 
%key insight behind the algorithm presented by Lowe in 
%\cite{lowe2004sift}.  However the implication doesn't follow the other 
%way around. In the case that a feature point doesn't have a true 
%correspondence there might still exist point with which the feature 
%point is uniquely matched. The issue is particularly pronounced if we 
%compare two images that do not correspond. For any proposed 
%correspondence it is entirely probable that this correspondence is 
%unique even if it isn't correct. When we match against the feature 
%points of both images this ambiguity is avoided.  When the two images 
%have no overlap or objects in common, chances are that a feature point 
%will match better with another feature point from the same image in 
%which case it is easily discarded.
%Often images will contain repetitive patterns that are difficult to 
%match\footnote{In fact this particular problem has been given attention 
%before by for example \cite{fan2011towards}} because the feature 
%descriptors covering these patterns will be similar. If we remove points 
%that aren't deemed sufficiently unique like in \emph{MM} this means that 
%these points will often be discarded even if they are correctly matched.
%\emph{MMC} makes it possible to look at groups of similar feature points 
%one at a time and within each group find the best matches. This is done 
%by taking the set of feature points from both images and cluster them by 
%their similarity. In some cases the clustering will end up grouping 
%feature points of only one image together which can then easily be 
%discarded in the matching process.  In other cases partitions will 
%contain similar feature points from both images that can then be matched 
%using \emph{MM} but with much lower thresholds.
\section{Matching Methods}

@@

@@

that match two points within the same image. In algorithm \ref{alg-mm} 
the implementation of \emph{MM} is shown.

@@

\caption{Mirror Match Algorithm (\emph{MM})}

@@

{\fontsize{10}{10}\selectfont

@@

\Require $images$ : set of images, $t$ : float $\in \mathbb{R}$

@@

\ForAll{$I_i \in images$} \Comment Gather Stage

@@

\ForAll{$f_i \in features$} \Comment Match Stage

@@

}

@@

In the acquisition state we gather all features in the set of images.  
These features are then matched in the match stage using K-Nearest 
Neighbors.  For any given feature $f_i$ the two most similar neighbors 
are returned and we calculate the ratio between them as as proposed in 

@@

\begin{figure*}
	\makebox[\textwidth][c]{%
		\begin{subfigure}[t]{0.32\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
			\caption{Source image}
			\label{fig:pitts_source}
		\end{subfigure}%
		\enspace %
		\begin{subfigure}[t]{0.32\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
			\caption{Keypoints Displayed}
			\label{fig:pitts_keypoints}
		\end{subfigure}%
		\enspace %add desired spacing between images, e. g. ~, \quad, 
		%\qquad (or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{0.32\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/mirror_match_off}
			\caption{\emph{SIFT}}
			\label{fig:unique}
		\end{subfigure}%
	}
	\makebox[\textwidth][c]{%
		\begin{subfigure}[t]{0.32\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
			\caption{\emph{MM} with intra image matches}
			\label{fig:within}
		\end{subfigure}%
		\enspace %add desired spacing between images, e. g. ~, \quad, 
		%\qquad (or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{0.32\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/mirror_match}
			\caption{\emph{MM}}
			\label{fig:without}
		\end{subfigure}%
		\enspace%
		\begin{subfigure}[t]{0.32\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/MMC_partition}
			\caption{\emph{MMC} Partition Example}
			\label{fig:pitts_partition}
		\end{subfigure}%
	}%
	\caption{Illustration of matches filtered by \emph{MM}. For each 
	correct match found between the two images, a green line is shown.  
Incorrect matches are marked with a red line. Figure \ref{fig:within} 
shows the correspondences found by mirror match, but including all 
matches that are found within the same image. }%
	\label{fig:comparemirror}%
\end{figure*}%

In figure \ref{fig:within} and \ref{fig:without} an example of the 
result of \emph{MM} is illustrated. In figure \ref{fig:unique} many of 
the incorrect matches occur in the fence in the bottom of the image.  
When we match all feature points together many of these incorrect 
matches are eliminated because points in the fence match with other 
points in the fence in the same image as shown in figure 
\ref{fig:within} and \ref{fig:without}.

\subsection{Mirror Match with Clustering (\emph{MMC})}
%
As opposed to \emph{MM}, \emph{MMC} diverges from traditional 
non-geometric feature matching by clustering the feature points by 
similarity. This process yields partitions of fairly similar feature 
points that we can match using the same approach as \emph{MM}. 
%
%Before we introduce the implementation details we will go over the 
%problem of graph clustering and how it relates to feature matching.
%
%\subsubsection{Graph Clustering}
%
%Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
%\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
%function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
%points in an image and returns their matching score, we can define a 
%matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
%as the \emph{adjecency matrix} of the fully connected graph where each 
%vertex corresponds to a keypoint and the edge between two vertices has a 
%weight equal to the distance between the two corresponding keypoints.
%
%This representation reduces the problem of partitioning the keypoints 
%into groups to that of graph clustering or community structure depending 
%on the context. In the literature there are various ways of clustering a 
%graph according to different measures of what constitutes an optimal 
%partitioning. Traditionally the most used clustering algorithms have 
%been K-means and spectral clustering, but in recent years a host of new 
%algorithms have been proposed based on both Newman's concept of graph 
%modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
%\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
%well as information theoretical measures\footnote{See for example 
%\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
%in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
%new algorithms differ from K-means clustering and Spectral clustering 
%in that they do not require the number of expected to clusters to be 
%specified beforehand\footnote{Among the aforementioned methods, this is 
%true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
%tests done using randomly generated graphs with a known partitioning 
%\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
%markedly better than spectral clustering and 
%K-means\cite{lancichinetti2009}.
%
%The performance of clustering algorithms is a complicated issue, since 
%an optimal clustering given the same graph can vary depending on the 
%application. Spectral clustering for example will usually return a 
%partitioning where each partition is roughly equal in size\footnote{As 
%mentioned in \cite{von2007}} while the Louvain 
%clustering\cite{blondel2008} might return partitions of very uneven 
%size, even if the modularity measurement has been shown to penalize very 
%small clusters\cite{brandes2007}. Both behaviours can be beneficial 
%depending on the application, but when clustering feature points, 
%maintaining clusters of an even size usually means that some clusters 
%will be '\emph{catch-all}' clusters where the feature points that do 
%not fit anywhere else are grouped together. The necessity of specifying 
%the amount of partitions in for example Spectral clustering or Pott's 
%model clustering further exacerbates the issue since smaller partitions 
%are then combined into one to achieve the right amount of partitions.

We use the Louvain Method\cite{blondel2008} for clustering feature 
points since it's relatively fast and performs 
well\cite{lancichinetti2009}, doesn't require 
parameters\cite{blondel2008} and doesn't emphasize partitions of equal 
sizes as opposed to for example spectral clustering and 
k-means\cite{von2007}.
%
\begin{algorithm}
\caption{Mirror Match with Clustering Algorithm (\emph{MMC})}
\label{alg-mmc}
{\fontsize{10}{10}\selectfont
\begin{algorithmic}
\Require $images$ : set of images, $t \in \mathbb{R}$
\State $M\gets \varnothing$
\State $F\gets \varnothing$
\ForAll{$I_i \in images$} \Comment Gather features
	\State $f_i\gets getFeatures(I_i)$
	\State $F\gets F \cup f_i$
\EndFor
\State $A\gets getAdjecencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
\State $A_{norm}\gets 1 - normalize(A)$
\State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
\State $P\gets cluster(A_{pruned})$
\ForAll{$p \in P$} \Comment p is a set of feature points
	\State $M\gets M \cup getMatches(p, t, F)$
\EndFor \\
\Return matches
\end{algorithmic}
}
\end{algorithm}

While the louvain clustering algorithm doesn't require any parameters in 
itself, it tends towards clustering all feature points together in the 
same partition if the graph is very connected.  To ensure that the graph 
is well clustered, the adjacency matrix is pruned so only edges above a 
certain threshold is kept. From empirical analysis keeping the 2.5\% of 
edges with the highest similarity seems to work well in practice. Figure 
\ref{fig:graph} shows the result of clustering the feature points 
displayed as a graph.
%
\begin{SCfigure*}
	\makebox[0.7\textwidth][c]{%
		\begin{subfigure}[t]{0.35\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/MMC_graph_full}
			\caption{Full Graph}
			\label{fig:full_graph}
		\end{subfigure}%
		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
		%(or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{0.32\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/MMC_graph_cropped}
			\caption{Cropped Section of Graph}
			\label{fig:cropped_graph}
		\end{subfigure}%
	}%
	\caption{The partitioned feature graph. Each vertex represents a 
		feature point while an edge represent a high similarity between 
		points. A partition is a connected group marked by a color.  Due 
		to a limited amount of colors some disconnected partitions have 
		been assigned the same color. The edge color of each node 
		signifies which image it belongs to. In the detailed crop to the 
		right the various cluster sizes can be seen, ranging from 
	hundreds of feature points to only two or three.}
	\label{fig:graph}
\end{SCfigure*}

>>>>

\documentclass[conference]{IEEEtran}
%\documentclass{article}
\usepackage{footnote}
%\usepackage[font={small}]{caption}
%\usepackage{sidecap}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
%\usepackage[stable]{footmisc}
%\usepackage{caption}
%\usepackage{adjustbox}
\usepackage{subcaption}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amssymb}

@@

\title{Mirror Match: Reliable Feature Point Matching Without Geometric Constraints}
\author{Anonymous ACPR Submission}

\maketitle
%
\begin{abstract}
Many algorithms have been proposed to solve the problem of matching 
feature points in two or more images using geometric assumptions to 
increase the robustness of the matching. However, very little work 
addresses the case where these assumptions might not hold. In particular 
few methods address the problem of reliable matching in cases where it 
is unknown whether two images have any corresponding areas or objects in 
the first place.

We propose two algorithms for matching feature points without the use of 
geometric constraints. The first relies on the fact that any match 
between two images should be better than all possible matches within a 
single image. The second algorithm extends this idea by using community 
structure in the similarity graph of feature points to find reliable 
correspondences. To evaluate the algorithms experimentally, we introduce 
a simple method to generate a large amount of test cases based on a set 
of image pairs with viewpoint changes. Our results show that the 
proposed algorithm is generally superior to traditional approaches in 
finding correct correspondences.

@@

at the geometric configuration of feature points and match them based on 
various assumptions about the geometric relationship between the images. 
These assumptions are then used to create different constraints on the 
matches, e.g.\ angular constraints \cite{kim2008efficient}, epipolar 
constraints \cite{torr2000mlesac,chum2005matching}, or pairwise 
constraints \cite{choi2009robust,leordeanu2005spectral}.

@@

%only consider matches that aren't   too much with respect to the 
%average angle and distancen as considered by \cite{kim2008efficient}.  
%This performs well in situations where no camera rotation occurs 
%between the two images, but fails when this assumption isn't met. 
%Various scenarios have been proposed to improve on this simple 
%assumption such as epipolar constraints (\cite{torr2000mlesac}, 
%\cite{chum2005matching}) and pairwise constraints 
%(\cite{choi2009robust}, \cite{leordeanu2005spectral}). The Epipolar 
%constraint carries the assumption that the two images matched are 
%related by an affine transformation. That is, there is no relative 

@@

An alternative is to pick out different areas in each image and pair 

@@

not fall within paired areas. Examples include \emph{Isodata} 
\cite{das2008event}, which clusters feature points according to their 
position in the image,
and the method from \cite{wu2011robust}, which uses maximally stable 
extremal regions (MSER) feature points to designate areas. %In this 
paper the algorithm from \cite{das2008event} will later be referred to 
as \emph{Isodata}.

@@

In practice there are many situations where relying on the geometry of the 
image to filter correspondences is not possible, for example images without overlap, or adjacent objects in one image are that are separated in 
another.  %Another example is images that do not overlap where algorithms might still find matches adhering to the imposed geometric constraints.
Furthermore, methods using geometric constraints all require an initial 
set of correspondences. If this set of correspondences can be narrowed down 
to the most probable correct matches, the geometric matching algorithm will benefit in terms of speed and accuracy. 
Finally some use cases might require a speed that simply cannot be achieved by 
complex geometric methods.% where simple non geometric methods might be able to provide sufficient matching accuracy with a smaller performance penalty.

In the absence of geometric constraints, only few methods are available. 
As pointed out in \cite{szeliski2010}, the simplest 
approach to matching feature points is to return all matches above a given 
threshold of similarity.  This can be done with a fixed threshold or by 
finding the nearest neighbors for each point (still filtering by a threshold to avoid including matches for feature points that have no counterpart in the other image).  
Lowe \cite{lowe2004sift} proposed the scale-invariant feature transform (SIFT) together with 
an alternative measure, where the uniqueness of a given match is found by 
looking at the two nearest neighbors of each feature point and 
calculating the matching score as the ratio of similarities.  Ranking the 
scores by their uniqueness and picking the $n$ best produces a set of 
correspondences that are distinctly matched across two images. %This method will be referred to as \emph{SIFT} in this paper. 
Of these three methods (fixed threshold, nearest neighbors, and \emph{SIFT}), 
\emph{SIFT} was found to perform best by a slight margin 
\cite{mikolajczyk2005performance}.

The two methods we propose in this paper are inspired by a simple 
but novel idea. If a given feature point in one image is better matched with other feature points from the 
\emph{same} image than points in the other image, then any matches from 
this feature point to points in the other image are considered unreliable and should be 
discarded.  This approach carries no implicit assumptions about the 
geometric consistency of matches and as such can easily be extended with 
other geometric solutions when appropriate or necessary.

Based on this idea,  we determine reliable matches as 
follows. \emph{Mirror Match (MM)} matches every feature from both 
images with all other features and filters matches based on the ratio of 
best to second best match as in \emph{SIFT}. \emph{Mirror Match with 
Clustering (MMC)} on the other hand takes the combined set of feature 
points from both images and clusters these points according to their 
descriptors.  If a resulting partition contains only feature points from one image, no matches are 
returned.  If the 
partition contains points from both images, \emph{Mirror Match} is used 
to find the best matches within this partition.  The experimental results 
show that both approaches generally outperform existing 
correspondence matching methods.

%Matching feature points against the entire set of points from both 
%images ensures that the distinctiveness of a returned correspondence is 
%higher. In almost all cases\footnote{Exceptions would include cases 
%where we want to find all particular points in a pattern and other use 
%cases where the correspondence isn't assumed to be unique}, a good 
%match between two images is unambiguous in the sense that there are no 
%other equally good potential matches to the same point.  This is the 
%key insight behind the algorithm presented by Lowe in 
%\cite{lowe2004sift}.  However the implication doesn't follow the other 
%way around. In the case that a feature point doesn't have a true 
%correspondence there might still exist point with which the feature 
%point is uniquely matched. The issue is particularly pronounced if we 
%compare two images that do not correspond. For any proposed 
%correspondence it is entirely probable that this correspondence is 
%unique even if it isn't correct. When we match against the feature 
%points of both images this ambiguity is avoided.  When the two images 
%have no overlap or objects in common, chances are that a feature point 
%will match better with another feature point from the same image in 
%which case it is easily discarded.
%
%Often images will contain repetitive patterns that are difficult to 
%match\footnote{In fact this particular problem has been given attention 
%before by for example \cite{fan2011towards}} because the feature 
%descriptors covering these patterns will be similar. If we remove points 
%that aren't deemed sufficiently unique like in \emph{MM} this means that 
%these points will often be discarded even if they are correctly matched.
%\emph{MMC} makes it possible to look at groups of similar feature points 
%one at a time and within each group find the best matches. This is done 
%by taking the set of feature points from both images and cluster them by 
%their similarity. In some cases the clustering will end up grouping 
%feature points of only one image together which can then easily be 
%discarded in the matching process.  In other cases partitions will 
%contain similar feature points from both images that can then be matched 
%using \emph{MM} but with much lower thresholds.
%

The paper is organized as follows.  Section~\ref{S:MatchingMethods} describes the proposed \emph{Mirror Match (MM)} and \emph{Mirror Match with Clustering (MMC)} algorithms.  Section~\ref{S:Experiments} presents the dataset used for evaluation and the experimental setup.  Section~\ref{S:Results} discusses the benchmarking results obtained.  Section~\ref{S:Summary} concludes the paper.

\section{Matching Methods}
\label{S:MatchingMethods}

@@

\begin{figure}
	\centering%
		\begin{subfigure}[t]{\columnwidth}
			\centering
			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_source}
			\caption{Source image pair}
			\label{fig:pitts_source}
		\end{subfigure}%
		\\ %
		\begin{subfigure}[t]{\columnwidth}
			\centering
			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_keypoints}
			\caption{Feature points}
			\label{fig:pitts_keypoints}
		\end{subfigure}%
		\\ %add desired spacing between images, e. g. ~, \quad, 
		%\qquad (or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{\columnwidth}
			\centering
			\includegraphics[width=0.85\columnwidth]{images/mirror_match_off}
			\caption{\emph{SIFT}}
			\label{fig:unique}
		\end{subfigure}%
		\\ %add desired spacing between images, e. g. ~, \quad, 
		\begin{subfigure}[t]{\columnwidth}
			\centering
			\includegraphics[width=0.85\columnwidth]{images/mirror_match_with_pruned}
			\caption{\emph{MM} intermediate result}
			\label{fig:within}
		\end{subfigure}%
		\\ %add desired spacing between images, e. g. ~, \quad, 
		%\qquad (or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{\columnwidth}
			\centering
			\includegraphics[width=0.85\columnwidth]{images/mirror_match}
			\caption{\emph{MM} final result}
			\label{fig:without}
		\end{subfigure}%
		\\ %add desired spacing between images, e. g. ~, \quad, 
		\begin{subfigure}[t]{\columnwidth}
			\centering
			\includegraphics[width=0.85\columnwidth]{images/MMC_partition}
			\caption{\emph{MMC} Partition Example}
			\label{fig:pitts_partition}
		\end{subfigure}%
	\caption{Feature matching with \emph{MM} and \emph{MMC}. Dots represent feature points; green/red lines indicate correct/incorrect matches, respectively; black lines represent edges in the feature graph.  
	(c) Result of \emph{SIFT} matching. 
  (d) All matches found by \emph{MM}, including intra-image matches. 
	(e) Final \emph{MM} result. 
	(f) Example of a partition of feature points after clustering, which 
includes similar feature points from building windows and shirt patterns.}%
	\label{fig:comparemirror}%
\end{figure}%

@@

that match two points within the same image. Algorithm~\ref{alg-mm} details  
the implementation of \emph{MM}.

@@

\caption{Mirror Match (\emph{MM})}

@@

%{\fontsize{10}{10}\selectfont

@@

\Require $images$ : set of images, $t \in \mathbb{R}$

@@

\ForAll{$I_i \in images$} \Comment Acquisition Stage

@@

\ForAll{$f_i \in features$} \Comment Matching Stage

@@

%}

@@

In the acquisition stage we gather all features in the set of images.  
In the matching stage these features are matched using $k$-nearest 
neighbors.  For any given feature $f_i$ the two most similar neighbors 
are returned, and we calculate the ratio between them as proposed in 

@@

%\begin{figure*}
%	\makebox[\textwidth][c]{%
%		\begin{subfigure}[t]{0.32\textwidth}
%			\centering
%			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
%			\caption{Source image pair}
%			\label{fig:pitts_source}
%		\end{subfigure}%
%		\enspace %
%		\begin{subfigure}[t]{0.32\textwidth}
%			\centering
%			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
%			\caption{Feature points}
%			\label{fig:pitts_keypoints}
%		\end{subfigure}%
%		\enspace %add desired spacing between images, e. g. ~, \quad, 
%		%\qquad (or a blank line to force the subfigure onto a new line)
%		\begin{subfigure}[t]{0.32\textwidth}
%			\centering
%			\includegraphics[width=\textwidth]{images/mirror_match_off}
%			\caption{\emph{SIFT}}
%			\label{fig:unique}
%		\end{subfigure}%
%	}
%	\makebox[\textwidth][c]{%
%		\begin{subfigure}[t]{0.32\textwidth}
%			\centering
%			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
%			\caption{\emph{MM} intermediate result}
%			\label{fig:within}
%		\end{subfigure}%
%		\enspace %add desired spacing between images, e. g. ~, \quad, 
%		%\qquad (or a blank line to force the subfigure onto a new line)
%		\begin{subfigure}[t]{0.32\textwidth}
%			\centering
%			\includegraphics[width=\textwidth]{images/mirror_match}
%			\caption{\emph{MM} final result}
%			\label{fig:without}
%		\end{subfigure}%
%		\enspace%
%		\begin{subfigure}[t]{0.32\textwidth}
%			\centering
%			\includegraphics[width=\textwidth]{images/MMC_partition}
%			\caption{\emph{MMC} Partition Example}
%			\label{fig:pitts_partition}
%		\end{subfigure}%
%	}%
%	\caption{Illustration of feature matching with \emph{MM} and \emph{MMC}. Dots represent feature points; green/red lines indicate %correct/incorrect matches, respectively; black lines represent edges in the feature graph.  
%(c) Result of \emph{SIFT} matching the two images.% 
%  (d) All matches found by \emph{MM}, including matches between points in the same image. 
%	(e) Final \emph{MM} result with the intra-image matches removed. 
%	(f) Example of a partition of feature points after clustering. This partition 
%includes similar feature points around the windows of a building and the patterns of a shirt.}%
%	\label{fig:comparemirror}%
%\end{figure*}%

Figure~\ref{fig:comparemirror} illustrates the benefits of \emph{MM} using an example image pair from the Gallagher dataset \cite{gallagher2008}.
With \emph{SIFT} (Figure~\ref{fig:unique}), many incorrect matches occur 
in the fence towards the bottom of the image.
When we match all feature points together, many of these incorrect 
matches are eliminated, because points in the fence match with other 
points in the fence in the same image (Figures~\ref{fig:within} and
\ref{fig:without}).

\subsection{Mirror Match with Clustering (\emph{MMC})}
%
In contrast to \emph{MM}, \emph{MMC} diverges from traditional 
non-geometric feature matching by clustering feature points by 
similarity. This process yields partitions of fairly similar feature 
points that we can match using the same approach as \emph{MM}.  
Algorithm~\ref{alg-mmc} shows the pseudocode implementation of \emph{MMC}.
%
%Before we introduce the implementation details we will go over the 
%problem of graph clustering and how it relates to feature matching.
%
%\subsubsection{Graph Clustering}
%
%Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
%\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
%function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
%points in an image and returns their matching score, we can define a 
%matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
%as the \emph{adjecency matrix} of the fully connected graph where each 
%vertex corresponds to a keypoint and the edge between two vertices has a 
%weight equal to the distance between the two corresponding keypoints.
%
%This representation reduces the problem of partitioning the keypoints 
%into groups to that of graph clustering or community structure depending 
%on the context. In the literature there are various ways of clustering a 
%graph according to different measures of what constitutes an optimal 
%partitioning. Traditionally the most used clustering algorithms have 
%been K-means and spectral clustering, but in recent years a host of new 
%algorithms have been proposed based on both Newman's concept of graph 
%modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
%\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
%well as information theoretical measures\footnote{See for example 
%\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
%in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
%new algorithms differ from K-means clustering and Spectral clustering 
%in that they do not require the number of expected to clusters to be 
%specified beforehand\footnote{Among the aforementioned methods, this is 
%true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
%tests done using randomly generated graphs with a known partitioning 
%\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
%markedly better than spectral clustering and 
%K-means\cite{lancichinetti2009}.
%
%The performance of clustering algorithms is a complicated issue, since 
%an optimal clustering given the same graph can vary depending on the 
%application. Spectral clustering for example will usually return a 
%partitioning where each partition is roughly equal in size\footnote{As 
%mentioned in \cite{von2007}} while the Louvain 
%clustering\cite{blondel2008} might return partitions of very uneven 
%size, even if the modularity measurement has been shown to penalize very 
%small clusters\cite{brandes2007}. Both behaviours can be beneficial 
%depending on the application, but when clustering feature points, 
%maintaining clusters of an even size usually means that some clusters 
%will be '\emph{catch-all}' clusters where the feature points that do 
%not fit anywhere else are grouped together. The necessity of specifying 
%the amount of partitions in for example Spectral clustering or Pott's 
%model clustering further exacerbates the issue since smaller partitions 
%are then combined into one to achieve the right amount of partitions.
%

%
\begin{algorithm}
\caption{Mirror Match with Clustering (\emph{MMC})}
\label{alg-mmc}
%{\fontsize{10}{10}\selectfont
\begin{algorithmic}
\Require $images$ : set of images, $t \in \mathbb{R}$
\State $M\gets \varnothing$
\State $F\gets \varnothing$
\ForAll{$I_i \in images$} \Comment Gather features
	\State $f_i\gets getFeatures(I_i)$
	\State $F\gets F \cup f_i$
\EndFor
\State $A\gets getAdjacencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
\State $A_{norm}\gets 1 - normalize(A)$
\State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
\State $P\gets cluster(A_{pruned})$
\ForAll{$p \in P$} \Comment p is a set of feature points
	\State $M\gets M \cup getMatches(p, t, F)$
\EndFor \\
\Return matches
\end{algorithmic}
%}
\end{algorithm}

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.8\columnwidth}
		\includegraphics[width=\columnwidth]{images/MMC_graph_full}
		\caption{Full Graph}
		\label{fig:full_graph}
	\end{subfigure}%

	%add desired spacing between images, e. g. ~, \quad, \qquad		  
	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}{0.7\columnwidth}
		\includegraphics[width=\columnwidth]{images/MMC_graph_cropped}
		\caption{Cropped Section of Graph}
		\label{fig:cropped_graph}
	\end{subfigure}%
	\caption{The partitioned feature graph (a). Each vertex represents a 
		feature point; lines indicate high similarity between 
		points. A partition is a connected group with the same color. The border color of each node 
		indicates which image it belongs to.  Zooming into a section of the graph (b), the various cluster sizes can be seen, ranging from 
	hundreds of feature points to only two or three.}
	\label{fig:graph}
\end{figure}

We use the Louvain Method \cite{blondel2008} for clustering feature 
points, since it is relatively fast and performs 
well \cite{lancichinetti2009}, does not require 
parameters \cite{blondel2008}, and does not emphasize partitions of equal 
size, as opposed to spectral clustering or 
k-means \cite{von2007}, for example.
While the Louvain clustering algorithm does not require any parameters in 
itself, it tends towards clustering all feature points together in the 
same partition if the graph is very connected.  To ensure that the graph 
is well clustered, the adjacency matrix is pruned so that only edges above a 
certain threshold are kept. From empirical analysis, retaining the top 
2.5\% of edges with the highest similarity seems to work well in 
practice. Figure~\ref{fig:graph} shows the result of clustering the 
feature points as a graph.
%
